\section{Agents in Kairi Field Theory}

\subsection{Definition}

In Kairi Field Theory (KFT), an \emph{agent} is defined as a locally coherent,
self-updating computational structure embedded within an AC--driven oscillatory
substrate. Formally:

\begin{equation}
    A := \langle S, R, U \rangle
\end{equation}

where:
\begin{itemize}
    \item $S$ is the agent's internal state space.
    \item $R$ is the rule-set (transition dynamics).
    \item $U$ is the update interface between the agent and the universal substrate.
\end{itemize}

\subsection{Oscillatory Computation}

All agents operate within a ternary oscillatory framework. Each computational
step consists of three phases:

\begin{equation}
    \Phi = \{ \phi_{+}, \phi_{0}, \phi_{-} \}
\end{equation}

representing reinforcement, neutrality, and opposition, respectively.

The universal computer is AC-driven, so each agent's update depends not on a
binary valuation but on the relative phase differences:

\begin{equation}
    \Delta \phi = \phi_{\text{incoming}} - \phi_{\text{internal}}.
\end{equation}

\subsection{Agent Update Rule}

Let $A_t$ denote the agent configuration at time $t$.  
Let $I_t$ denote the incoming signal from the universal substrate.

The update rule is:

\begin{equation}
    A_{t+1} = U(A_t, I_t)
\end{equation}

with $U$ constrained by ternary logic:

\begin{equation}
U: S \times \Phi \rightarrow S
\end{equation}

subject to the coherence condition:

\begin{equation}
    C(A_{t+1}) \geq C(A_t) - \epsilon,
\end{equation}

where $C(\cdot)$ is a ternary coherence functional and $\epsilon$ is the
permitted dissipation (environmental noise).

\subsection{Distinction-Making}

Agents create structure through distinction-making.  
A distinction is defined as:

\begin{equation}
    d: S \rightarrow \{+1, 0, -1\}
\end{equation}

representing a ternary categorization of states:
\begin{itemize}
    \item $+1$ (reinforce)
    \item $0$ (ignore)
    \item $-1$ (oppose)
\end{itemize}

Distinctions propagate when communicated to neighboring agents via the rule:

\begin{equation}
    R(A_i, A_j) = d_i \cdot \Delta \phi_{ij}
\end{equation}

where $\Delta \phi_{ij}$ captures phase difference between agents $i$ and $j$.

\subsection{Self-Reference and Form}

Self-reference is admissible in ternary systems. An agent $A$ may include its own
transition description within its state space:

\begin{equation}
    A = \langle S, R(S), U \rangle.
\end{equation}

This creates stable form when the update dynamics reach a fixed-point attractor:

\begin{equation}
    A^* = U(A^*, I^*)
\end{equation}

where $A^*$ is self-consistent under ternary oscillatory update.

\subsection{Interaction Network}

Let the set of all agents be $\mathcal{A}$.  
Agent interactions form a directed ternary network:

\begin{equation}
    \mathcal{G} = (\mathcal{A}, E, \Phi)
\end{equation}

where each edge $e_{ij}$ carries a ternary phase value:

\begin{equation}
    e_{ij} \in \Phi = \{+1, 0, -1\}.
\end{equation}

Updates propagate along $\mathcal{G}$ according to:

\begin{equation}
    A_i(t+1) = U\left(A_i(t), \sum_{j} e_{ji}(t)\right).
\end{equation}

\subsection{Agency as Game-Theoretic Play}

Agents act to maximize local coherence subject to global constraints.  
We define a ternary payoff functional:

\begin{equation}
    \Pi(A_i) = \sum_{j} f(e_{ij}, e_{ji})
\end{equation}

with

\begin{equation}
    f(e_{ij}, e_{ji}) =
    \begin{cases}
        +1 & \text{if phases mutually reinforce} \\
        0  & \text{if neutral} \\
        -1 & \text{if opposed}
    \end{cases}
\end{equation}

This yields a natural game-theoretic attractor dynamic:

\begin{equation}
    A_i(t+1) = \arg\max_{A_i'} \Pi(A_i').
\end{equation}

\subsection{Summary}

Agents in KFT:
\begin{itemize}
    \item are oscillatory, ternary computational units,
    \item make distinctions to shape local structure,
    \item update via phase-difference interactions,
    \item can self-reference without collapse,
    \item form stable patterns via attractor dynamics,
    \item behave game-theoretically to maximize coherence.
\end{itemize}

